### 2016-03-14 paper/result_stereo.tex

\noindent We have chosen 7 images with the resolution of $695\times555$
from the Book sequence of Middlebury stereo dataset for our
experiment~\cite{middlebury_stereo}. The number of disparity labels is
set to 256.
%
Since the order of labels is important for the expansion techniques,
we have used the same random order for all algorithms to avoid any
bias.
%
% In PAE, SF-MF, SF-SS and SF algorithms, the proposal generator in each
% thread can only generate constant-label proposals within a evenly split
% subset of all labels.

@@

For an easy optimization problem such as stereo with strong unary terms
and submodular pairwise terms, our full architecture with solution
sharing and multiway fusion actually makes convergence slower due to the
overhead of fusion and multi-threading.

>>>>

\noindent We have chosen 7 images with the resolution of $695\times555$
from the Book sequence of Middlebury stereo dataset~\cite{middlebury_stereo} for our
experiment. The number of disparity labels is
set to 256.
%
Since the order of labels is important for the expansion techniques,
we have used the same random order for all algorithms to avoid any
bias.
%
% In PAE, SF-MF, SF-SS and SF algorithms, the proposal generator in each
% thread can only generate constant-label proposals within a evenly split
% subset of all labels.

@@

For an easy optimization problem such as stereo with strong unary terms
and submodular pairwise terms, our full architecture with solution
sharing and multi-way fusion actually makes convergence slower due to the
overhead of fusion and multi-threading.
